Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-07 gibbs.tex
conclusions rewritten

\section{Conclusions}
We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
We have modeled the process of water desalination by sequential combinations of two processes: 
(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
We estimated the energy consumption of the whole process for producing a liter of potable water from brine as $W^{id} =$ 38.2 J/l.
Let us compare this value with the energy cost of RO, which is around 20000 J/l.
We have shown that the propsed gel compression method can compete with modern technologies used in modern industry.

>>>>

\section{Conclusions}
We have modeled the compression of the polyelectrolyte gel in thermodynamic equilibrium with the supernatant aqueous solution of a limited amount.
We have shown that the compression of the gel decreases the supernatant salinity.
We employed this phenomenon for modeling the process of water desalination.
The desalination was done as a sequential combination of two processes:
(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity;
(2) compression of the gel in \emph{closed system}, when the gel exchanges ions with a small reservoir affecting its salinity.
We estimated the energy consumption needed for producing one liter of potable water from brine and have shown that the proposed gel compression method may compete with modern desalination technologies.
